\documentclass{resume}

\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}

\name{Saravanan Tirunelveli Kanthi}
\address{ stirunel@qti.qualcomm.com, (858)740-4758 }
\address{ 13920 Capewood Lane, Apt 280, San Diego, CA 92128  }

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document} 

  \begin{rSection}{Professional Summary}
    Embedded software engineer with 8+ years of experience in developing 
    Firmware/Low-level drivers for RF/Mobile communication chipsets catering to 
    WCDMA, LTE,\& NR-5G standards. Extensive experience in HW-SW systems 
    integration, HW-SW bring-up and debugging in RTOS environments.  
  \end{rSection}

  \begin{rSection}{Education}
    {\bf Georgia Institute of Technology, Atlanta, GA} 
    \hfill {\em Aug 2007 - Dec 2009} \\ 
    { M.S. in Electrical \& Computer Engineering } 
    \hfill {GPA: 3.64/4.00} \\
    Thesis: SAR A/D \& 3.5GHz RF Tx design in 90nm CMOS\\
    Link: https://smartech.gatech.edu/handle/1853/33884\\
    
    {\bf Anna University, Crescent Engineering College, Chennai, India} 
    \hfill {\em Aug 2002 - May 2006} \\ 
    { B.E. in Electronics \& Communication Engineering } 
    \hfill {GPA: 91\%} 
  \end{rSection}
 
  \begin{rSection}{Technical Strengths}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Programming Languages & C, C++ \& Python  \\
      Communication Protocols & WCDMA, DC-HSDPA, LTE, LAA, LTE-U \& 5G NR \\
      Embedded Processors & ARM v5, v7, v11, Cortex M3/M4 \& Q6-DSP\\
      Tools & Git, Vim, Emacs, Perforce, SlickEdit, GCC \& GDB \\
      Domain Knowledge & Embedded Systems, DSP, RF engineering \& ASIC design \\
    \end{tabular}
  \end{rSection}  
   
  \begin{rSection}{Professional Experience} 
    \begin{rSubsection}
    {Qualcomm Technologies, Inc}
    {Nov 2015 - Present}
    {Staff Engineer}
    {San Diego, CA}
    \item Defined the SW architecture for the receive chain operation in 5G NR 
    Sub6 and Millimeter-wave – in Qualcomm flagship 5G modems - SDX50 and SDX55.
    \item Established call flows and designed them to fit within the timeline 
    needs of 5G NR Millimeter-wave.
    \item Continuously worked with multiple teams - firmware, RF systems, 
    Modem systems - to understand the scope of any feature, design the call 
    flow, and set the expectation for deliverables.
    \item Designed SW task plans to project the resource needs to meet certain 
    milestones before the arrival of RF chipsets. 
    \item Developed SW drivers to control feedback loops like Rx AGC 
    (Automatic Gain control), AFC (Automatic frequency correction), and 
    Beam management.
    \item Developed FW drivers to precisely control the timing of each feedback 
    operation, in strict adherence to the tight timeline requirements of 5G NR.
    \item Core player in enabling LAA software developments and helped drive the 
    adoption of Qualcomm modem solutions with LTE-U/LAA technology.
    \item Developed LTE AS DIV (Antenna Switch Diversity) feature for customer 
    specific hardware suited to their unique requirements - Apple \& Samsung.
    \item Collaborate extensively with cross-functional teams in developing 
    features to utilize the new features offered by the chipset.
    \item Received 8+ Qualstar awards for outstanding contribution to 
    LTE/5G/WCDMA/IOT efforts.
    \end{rSubsection}
    
    \begin{rSubsection}
    {Qualcomm Technologies, Inc}
    {Nov 2012 - Nov 2015}
    {Senior Engineer}
    {San Diego, CA}
    \item Developed low-level device drivers for enabling 3G/4G mode of 
    operation in multiple RF chipsets RTR86xx, WTR16xx, WFR16xx, WTR39xx, and
    WTR5975.
    \item Designed a concurrency management module to facilitate Qualcomm 
    dual-sim features like DSDA, DSDS \& DR-DSDS.
    \item Designed \& developed the RFFE protocol interface for Qualcomm hardware 
    and established an acceptable metric for external vendor chipsets.
    \item Interact with customers to gather requirements for their specific 
    feature requests and design them. 
    \item Provide the first line of support to debug customer reported issues 
    reported from their field tests, and resolve them.
    \item Developed SW tools to automate testing of Qualcomm prototype device on 
    R\&S CMW 500 test platform.
    \end{rSubsection}    
  
    \begin{rSubsection}
    {Qualcomm Technologies, Inc}
    {June 2010 - Nov 2012}
    {Engineer}
    {San Diego, CA}
    \item Part of the WCDMA technology core team, designated to work closely 
    with customers to design, develop, bring-up, and debug RF device drivers.
    \item Developed low-level device drivers for Qualcomm multimode RF chipsets 
    with focus on 3G WCDMA/4G LTE.
    \item Develop WCDMA RF features as per customer requirements and RF systems 
    team recommendation.
    \item Performed RF board bring up for 3G/4G technologies.    
    \item Implemented process improvements for monitoring the Jenkins status and 
    health of RF drivers at any given point of time.    
    \end{rSubsection}   
      
    \begin{rSubsection}
    {Georgia Institute of Technology \- Electrical \& Computer Engineering}
    {Jan 2008 - Dec 2009}
    {Graduate Research Assistant}
    {Atlanta, GA}
    \item Performed measurements and characterization of RF chipsets in 
    Millimeter-wave frequencies.
    \item Developed SAR ADC circuit to pair with a 3.5 GHz Transmitter circuit 
    as a feeder circuit to 60 GHz transmitter. Verified this design on 90nm CMOS
    technology and presented as my thesis.
    \item Developed test framework, wrote embedded device drivers to probe the 
    Millimeter-wave test bed at various points and tap out the signals through 
    a GPIO. 
    \end{rSubsection}

    \begin{rSubsection}
    {Wipro Technologies}
    {August 2006 - June 2007}
    {Project Engineer}
    {Chennai, India}
    \item Debugged and resolved issued reported by customers using HP 
    multi-function printers.
    \item Developed the embedded drivers for the \'Auto-Resolve\' in MFP 
    (Multi-function printers),to automatically detect a paper-jam scenario and 
    fix the same.
    \item Managed integration of various software components for major software 
    updates to  enterprise HP printers.
    \end{rSubsection}  
  \end{rSection}
   
  \begin{rSection}{References}
    Available upon request. 
  \end{rSection}
   
\end{document}

